---
title: "Assignment_46174281_NgocThuyNguyen"
author: "Tracy"
date: "06/10/2021"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Question 1: 
 a) Produce a scatterplot and correlation matrix of the data and comment on possible relationships between the response and predictors and relationships between the predictors themselves.
```{r}
paramo =read.table("paramo.dat", header = TRUE)
pairs(paramo, panel= panel.smooth)
cor(paramo)
```
* From the scatterplot and correlation matrix, the response is correlated with other predictors and the predictors also have a correlation relationship with each of other predictors. 
b) Fit a model using all the predictors to explain the N abundance number response. Conduct an F -test for the overall regression
* The mathematical multiple regression model for this situation: $$Y= \beta_0+ AR\beta_1 +EL\beta_2+ DEc\beta_3+ DNI\beta_4 +\epsilon $$ with $$ \epsilon\sim N(0,\sigma^2)$$

```{r}
paramo.lm= lm(N ~ AR + EL + DEc + DNI , data = paramo)
summary(paramo.lm)
coefficients(paramo.lm)
```
- Line of Fit: $$Y= 27.89+ 5.154AR+ 3.075EL- 0.017DEc+ 0.0166DNI$$
* The Hypotheses for the Overall ANOVA test of multiple regression:
\begin{flalign*}
 H_0 &: \beta_1= \beta_2= \beta_3= \beta_4 = 0 & \\
 H_1 &: \beta_i \neq 0  
\end{flalign*}
* Produce an ANOVA table for the overall multiple regression model:
```{r}
anova(paramo.lm)
```
\begin{flalign*}
FullRegSS &= RegSS_AR+ RegSS_EL|AR+ RegSS_DEc|AR-EL+ RegSS_DNI|AR-EL-DEc & \\
            &= 508.92+ 45.9+ 537.39+ 2.06= 1094.27 
\end{flalign*}
\begin{flalign*}
RegM.S &= \frac{RegSS}{k} = \frac{1094.27}{4}= 273.567 &    
\end{flalign*}
* F-statistic:
\begin{flalign*}
F_obs &= \frac{Reg.M.S}{Res.M.S}= \frac{273.567}{44.95}= 6.086 &
\end{flalign*} 
* P-value:
\begin{flalign*}
P(F_3,10\geq 6.086) &= 0.01260809 < 0.05 &
\end{flalign*} 
* State the null distribution and conclusion:
  * Reject H_0 when F_obs is too large (>F_3,10)
  * According to P-value, reject H_0 at the 5% level -->there is a significant linear relationship between response and at least one of the four predictor variables.
c) Validate the full model using all the predictors and comment on whether it is appropriate to a multiple regression model to explain the N abundance value.
  


